---
title: "Biol 432 - Tutorial 4"
author: "Matthieu Tuffery"
date: "20309526"
output: html_document
---


### Project info:

date: 01/02/2022

github: MatthieuTu/A4_MatthieuTu.git

https://github.com/MatthieuTu/A4_MatthieuTu.git



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Code:

The objective of this code is to create a new csv file called "MeasShort.csv", containing the data from "measurements.csv" after modifying the format of the column "Organism".

First we load dplyr to access useful functions and we set the working directory. We load measurement.csv as a DataFrame "MData".
```{r, warning= FALSE, message=FALSE}
library(dplyr)

setwd("./")

MData = read.csv(file = "measurements.csv", header = T)
```

This chunk of code adds a new column "Sp" containing the first letter of the genus, a period and the species name.
```{r}
MData = mutate(MData, Sp =  sub(
                  "(\\w)\\w+", # we keep in memory the first letter, and we replace the first word by...
                  paste("\\1", ".", sep = ""), # ... the first letter followed by a period.
                  MData$Organism 
                              )
              )
```
We create a new dataframe and write a new csv file (MeasShort.csv) with the dataframe.
```{r}
ShortData = select(MData, Sp, everything(), -Organism)
write.csv(ShortData, file = "MeasShort.csv", row.names = F)
```

